---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can edit [this `.rmd` file](https://github.com/UBC-STAT/STAT545.github.io/blob/main/content/mini-data-analysis/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by:

-   Making summary tables and graphs
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.*

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class, and indicate *why* you had to deviate. Feel free to contact the instructor in these cases.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://github.com/UBC-STAT/STAT545.github.io/blob/main/content/mini-data-analysis/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission.

**Research Questions**: In Milestone 1, you chose four research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
# install.packages("here")
library(here)
library(broom)
TAD_data <- tibble(read.csv(here("data", "TAD_data_combined.csv"))) %>% mutate(surface_time = X0.1.m + X1.2.m, Ptt = as.factor(Ptt))
```

# Task 1: Process and summarize your data

From Milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (1 point)

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->

1.  Does the average proportion of time spent at different depths differ whale to whale?

2.  What is the relationship between the proportion of time spent at the surface and the time of day?

3.  What is the relationship between the proportion of time spent at the surface and the time of year?

4.  Does the proportion of time spent at deeper depths change with the time of day?

    <!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks:

8.  Create a graph that has at least two geom layers.
9.  Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

## Research question #1

```{r}
## Summarizing the number of observations for each whale ##
TAD_data_q1 <- TAD_data %>% group_by(Ptt) %>% summarize(count = length(surface_time))

print(TAD_data_q1)

## Graphing the data with multiple geom layers and different alpha values ##

plot1 <- ggplot(TAD_data, aes(x=Ptt, y=surface_time)) + 
  geom_violin() + geom_jitter(size=0.4, alpha=0.3)

print(plot1)

```

The summary table shows us that we have much more data for some whales than others, since the data is evenly spaced in time this means that some tags were recording over longer time periods. Covering a longer time period could explain differences in the distribution of time spent at the surface between the whales (see question 3).

The plot shows us that whale #128156 is a clear outlier, this could be due to a malfunctioning tag. Also, the distributions for #128161 and #128164 look slightly different from the others. The transparency of the points in the plot helps keep the focus on the violin plot.

The purpose of this research question was to determine if differences between individual whales can be ignored when looking at other data metrics. It appears as though they cannot.

## Research question #2

```{r}

## Summarizing by creating a categorical variable to bin the time data
TAD_data_q2 <- TAD_data %>% 
  mutate(Date = as.POSIXct(Date*60*60*24, origin = "1899-12-30", tz="Etc/GMT-6")) %>%
  mutate(Hour = hour(Date)) %>% 
  mutate(Hour_block = cut(Hour, breaks = c(0, 6, 12, 18, 24), include.lowest = TRUE, right=FALSE)) %>% 
  select(ID, Ptt, Date, Hour_block, surface_time) %>% group_by(Hour_block)

# Create histograms showing the distribution of surface_time during the different time blocks
plot2_5_bins <- ggplot(TAD_data_q2, aes(x=surface_time)) + geom_histogram(bins=5) + facet_grid(rows = TAD_data_q2$Hour_block) + labs(title="Distribution of surface time for four time of day blocks", x="Percentage of time at the surface")

plot2_20_bins <- ggplot(TAD_data_q2, aes(x=surface_time)) + geom_histogram(bins=20) + facet_grid(rows = TAD_data_q2$Hour_block) + labs(title="Distribution of surface time for four time of day blocks", x="Percentage of time at the surface")

plot2_100_bins <- ggplot(TAD_data_q2, aes(x=surface_time)) + geom_histogram(bins=100) + facet_grid(rows = TAD_data_q2$Hour_block) + labs(title="Distribution of surface time for four time of day blocks", x="Percentage of time at the surface")

print(TAD_data_q2)
print(plot2_5_bins)
print(plot2_20_bins)
print(plot2_100_bins)

```

Creating a categorical variable for time allows us to summarize our data more easily. The data was collected in 6 hour blocks, so it makes sense to treat time as discrete rather than continuous.

The histograms show us that the proportion of time spent at the surface is rather similar for each time block. Although it appears that whales are more likely to spend all of their time at the surface at night. The histogram with 20 bins is better than the others since it's the most bins we can use while still keeping the smooth appearance. Because we expect the distribution to be continuous, a smooth histogram means that we are not seeing as much of the effects of random noise in the data. The histogram with 100 bins shows a lot of peaks and valleys, but this is all noise.

The purpose of this question was to determine if belugas are more likely to be detected at the surface of the bay at different times of day. These results suggest that they are not, meaning that it doesn't matter what time of day the aerial survey is conducted.

## Question #3

```{r}
# Create tibble summarizing the data for each date
TAD_data_q3 <- TAD_data %>% mutate(Date = as.POSIXct(Date*60*60*24, origin = "1899-12-30", tz="Etc/GMT-6")) %>%
   filter(Date > as.Date("2015-07-10") & Date < as.Date("2015-11-01")) %>%
  mutate(Date = date(Date)) %>% group_by(Date) %>% 
  summarize(
    mean = mean(surface_time), 
    min = min(surface_time), 
    max=max(surface_time),
    median = median(surface_time),
    sd = sd(surface_time)
  )


# Plot the mean time at the surface versus date as well as the range
plot3 <- ggplot(TAD_data_q3, aes(x=Date)) +
  geom_ribbon(aes(ymin = min, ymax = max), fill = "grey70") + 
  geom_line(aes(y=mean)) +
  labs(title="Percentage of time at the surface vs date", y = "Percentage of time at the surface")

print(TAD_data_q3)
print(plot3)
```

The summary table shows us the mean, range, median, and standard deviation of time spent at the surface for each calendar date (across time blocks and individual whales). This table is not very useful since it has many rows.

The plot shows the mean time at the surface along with the range as a function of calendar date. This shows clearly how the belugas spend less time at the surface in the fall than they do during the summer.

The purpose of this question was to determine if how we interpret aerial survey results should depend on the date the survey was conducted. The result is that it should, since a survey conducted in October will miss many more whales than a survey conducted in July.

## Question #4

```{r}
# Create categorical variable for time of day block
TAD_data_q4 <- TAD_data %>% replace(is.na(.), 0) %>%
  mutate(time_below_10m = X10.20.m + X20.50.m + X50.100.m + X100.200.m +X200.300.m + X300.500.m + X500.700.m + X.700.m) %>%
  mutate(Date = as.POSIXct(Date*60*60*24, origin = "1899-12-30", tz="Etc/GMT-6")) %>%
  mutate(Hour = hour(Date)) %>% 
  mutate(Hour_block = cut(Hour, breaks = c(0, 6, 12, 18, 24), include.lowest = TRUE, right=FALSE)) %>% 
  select(ID, Ptt, Date, Hour_block, time_below_10m) %>% group_by(Hour_block)


# Plot histograms with different numbers of bins

plot4_5_bins <- ggplot(TAD_data_q4, aes(x=time_below_10m)) + 
  geom_histogram(bins=5) + 
  facet_grid(rows = TAD_data_q2$Hour_block) + 
  labs(title="Distribution of time spent below 10 m in depth", x="Percentage of time")

plot4_20_bins <- ggplot(TAD_data_q4, aes(x=time_below_10m)) + 
  geom_histogram(bins=20) + 
  facet_grid(rows = TAD_data_q2$Hour_block) + 
  labs(title="Distribution of time spent below 10 m in depth", x="Percentage of time")

plot4_100_bins <- ggplot(TAD_data_q4, aes(x=time_below_10m)) + 
  geom_histogram(bins=100) + 
  facet_grid(rows = TAD_data_q2$Hour_block) + 
  labs(title="Distribution of time spent below 10 m in depth", x="Percentage of time")

plot5 <- ggplot(TAD_data_q4, aes(x=Hour_block, y=time_below_10m)) + 
  geom_violin() + 
  geom_jitter(size=0.4, alpha=0.3) + 
  scale_y_log10() + 
  labs(title="Percentage of time spent below 10 m in depth vs time of day", x="Time of day", y="Percentage of time spent below 10 m in depth")

print(TAD_data_q4)
print(plot4_5_bins)
print(plot4_20_bins)
print(plot4_100_bins)

print(plot5)
```

Here I'm following a similar process to question 2, except I'm looking at the time spent below 10 m in depth rather than the time spent at the surface. The table isn't very useful for answering the question because it has thousands of rows.

The histograms provide a visual representation of the table. I think the histogram with 5 bins is the best in this case since it makes it easier to see the monotone decreasing trend in the histogram. I also included a violin plot with a scaled y axis to see if this made it easier to see any difference between the time blocks, but the plot is not very helpful due to all of the zero values.

The point of this question was to determine if belugas are more likely to be feeding at a particular time of day, but the results are inconclusive.

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->

I think for question one, the plot brings me slightly closer to answering the desired question. I can clearly see that one of the whales is an outlier, but I'll need more statistical analysis to determine if the differences between the others is significant.

For question two, the operations I did don't show any obvious trends so I will need to use more powerful methods. This question can be refined by specifying what sort of trend I am looking for. I could look for a linear trend here, but I think it would make more sense to look at each distribution independently and see if the differences are statistically significant.

Question three is the most interesting in my opinion. The plot shows a clear trend with the time of year, but again I was not specific enough in the question in what I meant by a trend. Here, I think it would be appropriate to look for a linear trend.

As with question two, I was unable to detect any differences between the groups with my question four plots. This could benefit from a parametric approach by modelling each distribution as an exponential and seeing if there are statistical differences in the rate.

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

To start with, I will reduce the number of columns.

```{r}
TAD_data_reduced <- TAD_data %>% select(Ptt, Date, X0.1.m, X1.2.m, X2.4.m, X4.5.m, X5.6.m, X6.10.m)

head(TAD_data_reduced)
```

The Ptt column is the ID number of the whale, this is a variable since we have 9 different whales with unique ID numbers. Each cell in this column contains a value.

The Date column is the date and time of the observation. Some of these are repeats (same date/time but different whale), so these could be refactored (I will explain later why this is a bad idea).

The depth bin columns each correspond to a depth range and they store the percentage of time each whale spent in that depth bin for each time block.

I think my data is tidy since each row is a distinct observation and the columns are all variables.

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

Although my data is tidy, one way it can be refactored is by grouping together dates and moving the Ptt column to the depth bin names. This groups observations with the same time stamp together, and reduces the number of rows in the table.

```{r}
untidied_data <- TAD_data_reduced %>% 
  pivot_wider(
    names_from = Ptt,
    values_from = c(X0.1.m, X1.2.m, X2.4.m, X4.5.m, X5.6.m, X6.10.m)
  )

head(untidied_data)
```

Doing this reduces the number of rows and gives us unique values in the Date column, but only by dramatically increasing the number of columns and making the table less readable. This also violates the tidiness principle that each row should correspond to an observation. Here we've grouped 9 observations (created by nine separate tags) into each row. Now I will tidy the data back to its original state.

```{r}
retidied_data <- untidied_data %>% 
  pivot_longer(
    starts_with("X"),
    cols_vary="slowest",
    names_to = c(".value", "Ptt"),
    names_sep = "_",
    values_drop_na = TRUE
  ) %>% 
  relocate(Ptt) %>%
  mutate(Ptt = as.factor(Ptt)) %>%
  arrange(Ptt, Date)

head(retidied_data)

# check if the tibble is equal to the original
print(all.equal(TAD_data_reduced, retidied_data))
```

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  What is the relationship between the proportion of time spent at the surface and the time of year?
2.  Does the proportion of time spent at deeper depths change with the time of day?

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

The first question I chose seems to be the most likely to generate interesting results based on the plots I made for task 1. The other three questions are all fairly similar, but the question I chose looks like it will be the easiest to parameterize since the distribution appears to follow a straightforward exponential.

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.)

<!--------------------------- Start your work below --------------------------->

For these questions I only need 4 columns: date, time of day, surface time, and time below 10 m in depth.

```{r}
TAD_data_task3 <- TAD_data %>% 
  mutate(Date = as.POSIXct(Date*60*60*24, origin = "1899-12-30", tz="Etc/GMT-6")) %>% # convert Date to a recognizable format
  filter(Date > as.Date("2015-07-10") & Date < as.Date("2015-11-01")) %>% # filter observations between July 10 and November 1
  mutate(Hour_block = cut(hour(Date), breaks = c(0, 6, 12, 18, 24), include.lowest = TRUE, right=FALSE)) %>% # change time of day to a factor with 4 six hour blocks
  mutate(Date = date(Date)) %>%  # remove the time of day from the date column
  replace(is.na(.), 0) %>% # replace NA with 0 (for the depth bins where no data was recorded)
  mutate(time_below_10m = X10.20.m + X20.50.m + X50.100.m + X100.200.m +X200.300.m + X300.500.m + X500.700.m + X.700.m) %>% # compute the percentage of time spent below 10 m in depth
  select(Date, Hour_block, surface_time, time_below_10m) # select only the needed columns

head(TAD_data_task3)
```

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: What is the relationship between the proportion of time spent at the surface and the time of year?

**Variable of interest**: surface_time

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->

I will use a glm to check for a trend. The most appropriate model here is a beta regression, but first I need to rescale the data.

```{r}
#install.packages("betareg") # package used for beta regression
#install.packages("scales") # package used for rescaling
library(betareg)
library(scales)

# rescale the surface time to be in (0,1) instead of [0, 100]
TAD_data_task3$surface_time <- rescale(TAD_data_task3$surface_time, to=c(0.001,0.999))
head(TAD_data_task3)

TAD_data_task3 <- mutate(TAD_data_task3, day_number = as.integer(Date - as.Date("2015-07-10"))) # rescale the date so that the intercept is at the start of the time series

# fit a beta glm to the data
fit <- betareg(surface_time ~ day_number, data = TAD_data_task3, link = "logit")
```

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

I think the relevant thing here is the p-value on the day_number coefficient.

```{r}
fit_tibble <- tidy(fit) # use the Broom package to summarize the model

# use the fitted model to get predicted surface time values for each date
predicted_df <- data.frame(
  surface_time_pred = predict(fit, TAD_data_task3), 
  day_number=TAD_data_task3$day_number
)

# plot the expected surface time versus date
plot <- ggplot(TAD_data_task3, aes(x=day_number, y=surface_time)) + 
  geom_point() + 
  geom_line(colour="red", aes(y=predicted_df$surface_time_pred)) + 
  scale_y_continuous(labels = percent) +
  scale_x_continuous(labels=c(
    "0" = "2015-07-10", 
    "30"=toString(as.Date("2015-07-10")+30), 
    "60"=toString(as.Date("2015-07-10")+60), 
    "90"=toString(as.Date("2015-07-10")+90)
  ), breaks=c(0,30, 60, 90)) +
  labs(
    title = "Percentage of time at surface versus time of year",
    x = "Date",
    y = "Percentage of time at surface"
  )

print(fit_tibble)
print(plot)
```

From this tibble we can see that the p-value on the day_number coefficient is exceedingly small (second row, sixth column of the tibble). The purpose of this question was to determine if how we interpret aerial survey results should depend on the date the survey was conducted. The result is that it should, since a survey conducted in October will miss many more whales than a survey conducted in July.

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

I will save the summary table created for question 3 in task 1.

```{r}
dir.create(here("output"))
write.csv(TAD_data_q3, here("output", "TAD_data_q3.csv"))
```

<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->

```{r}
saveRDS(TAD_data_q3, here("output", "TAD_data_q3.RDS")) # save the file to the output folder
TAD_data_RDS <- readRDS(here("output", "TAD_data_q3.RDS")) # read the file from the output folder

head(TAD_data_RDS)
```

<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors.

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone.

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files.
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2.
